Computer Science House Constitution

### 2022-03-23 constitution.tex
Clarifies the voting members must be Eboard

>>>>

	\item The date and time of candidate speeches will be announced by a member of the Executive Board at least five (5) days prior to the event. 
		All Active Members are expected to attend candidate speeches in accordance with \ref{Expectations of House Members}.
		If a member cannot attend due to a scheduling conflict, they may provide a reason for their absence to the Evaluations Director, who will record the reason with the absence.
